The 2014 SMT Competition

### 2015-08-04 2014/report/SMTCOMP.tex
added info in rules for SL-COMP, QBF

\paragraph{Scoring differences.} A more significant issue is how solver errors are taken into account in the metrics. A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature. Different competitions vary on this aspect. SMT-COMP has historically emphasized soundness; a
single error in a division caused the solver to be scored lower than any other solver with no errors, even if the other solvers solved very few problems. For the SAT competition, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}. In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).

>>>>

\paragraph{Scoring differences.} A more significant issue is how solver errors are taken into account in the metrics. A solver error indicates an unsoundness in the tool, which is highly undesirable; however, highly penalizing errors may discourage new entrants whose tools are not yet mature. Different competitions vary on this aspect. SMT-COMP has historically emphasized soundness; a
single error in a division caused the solver to be scored lower than any other solver with no errors, even if the other solvers solved very few problems. In its inaugural edition, the Separation Logic Competition (SL-COMP) adopted the same rules as SMT-COMP. For the SAT competition, however, an error outright disqualifies a tool in the category it occurs\footnote{See \url{http://satcompetition.org/2014/rules.shtml}.}. In the QBF Gallery, a competitive evaluation of solvers for Quantified Boolean Logic, the score is the number of solved instances. In contrast, in the SV-competition~\cite{svcomp-2015}, successful runs account positively towards the final score, while errors count negatively (with an increased weight).
